Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-16 forecast/paper/paper.tex
Update discussion (unfinished)

Can axuiliary indicators improve COVID-19 forecasting and hotspot prediction
models?  Our answer, based on analyzing five auxiliary indicators from the  
COVIDcast API (defined using from medical insurance claims, internet-based
surveys, and Google search trends) is undoubtedbly ``yes''. However, there are 
levels of nuance to such an answer that must be explained.  None of the
indicators that we have investigated appear to be the ``silver bullet'' that 
one  might have hoped for, revolutionizing the tractability of the prediction 
problem, rendering it ``easy'' when it was once ``hard'', in the absence of
auxiliary information.  Rather, the gains in accuracy offered by the indicator
models appear to be nontrivial, and consistent across modes of analysis, but
modest---and more about tipping the bias-variance tradeoff in our favor than
providing a consistent leading indication of future events.

[TODO:  Explain how insights from up/down/flat, lagging/leading, etc., are
relevant to this overall arc.  Reiterate the importance of vintage data.  Finish
with something about what's left for future work?  ]

>>>>

Can axuiliary indicators improve COVID-19 forecasting and hotspot prediction
models?  Our answer, based on analyzing five auxiliary indicators from the  
COVIDcast API (defined using from medical insurance claims, internet-based
surveys, and Google search trends) is undoubtedbly ``yes''. However, there are 
levels of nuance to such an answer that must be explained.  None of the
indicators that we have investigated appear to be the ``silver bullet'' that 
one  might have hoped for, revolutionizing the tractability of the prediction 
problem, rendering it easy when it was once hard (in the absence of auxiliary 
information).  Rather, the gains in accuracy offered by the indicator models 
(over an autoregressive model based on past case rates along) appear to be
nontrivial, and consistent across modes of analysis, but modest.  In
forecasting, the indicator models appear to be most useful in periods in which 
case rates are flat or trending down, rather than periods in which case rates
are trending up (as one might hope to see, as the hypothetical benefit provided
by an idealized ``leading indicator'').

As mentioned previously, the indicator models could certainly benefit from a 
careful handling of location-specific effects (to account for spatial
heterogeneity in the search trends and claims-based indicators in particular),
as well as nowcasting techniques to estimate finalized indicator values before
using them as features (to account for backfill in the claims-based indicators
in particular).  Beyond this, it is certainly possible that more sophisticated 
models for forecasting or hotspot prediction would lead to different results,
and potentially even different insights.  Natural directions to explore include  
using interactions, using multiple indicators in tandem in a single model, and 
leveraging HRR demographics or mobility patterns.  That said, we are doubtful
that the ``topline'' conclusion would change--that auxiliary indicators can
provide a nontrivial, consistent, but modest improvement in forecasting and
hotspot prediction.

Furthermore, from our experience working on forecasting  TODO

[  Finish by reiterating the importance of vintage data.  Emphasizing the rigor
or our approach, how we have provided a template for others to be able to do the
same thing with new models ]
